---
title: "p8105_hw6_wz2630"
output: github_document
---
```{r}
library(dplyr)
library(tidyverse)
library(modelr)
library(knitr)
```


# Problem 1
(omitted)


# Problem 2

## Dataset:
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

## Bootstrapping
The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response with tmin and prcp as the predictors, and are interested in the distribution of two quantities estimated from these data:

* r_hat^2
* log(beta_hat1*beta_hat2)

1. Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. 

2. Plot the distribution of your estimates, and describe these in words. 

3. Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r_hat^2 and log(beta_hat1*beta_hat2).
 
Note: broom::glance() is helpful for extracting r_hat^2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(beta_hat1*beta_hat2).
```{r}
set.seed(1)

n_samp = 5000

# define boot_sample function
boot_sample = 
  function(df) {sample_frac(df, replace = TRUE)}

# generate bootstrap samples
boot_straps = 
  tibble(strap_number = 1:5000) |> 
  mutate(
    strap_sample = map(strap_number, \(i) boot_sample(df = weather_df))
    )

boot_straps

# generate the estimates of interest
bootstrap_results = 
  boot_straps |> 
  mutate(
    models = map(strap_sample, \(df) lm(tmax ~ tmin+prcp, data = df) ),
    results_1 = map(models, broom::tidy),
    results_2 = map(models, broom::glance)) |> 
  select(-strap_sample, -models) |> 
  unnest(results_1, results_2) 

```


```{r}
# pivot results dataset
pivot_bootstrap_results = 
  bootstrap_results |> 
  select(strap_number, term, estimate, r.squared)|>
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) |> 
  mutate(quantity2 = ifelse(tmin * prcp <= 0, NA, log(tmin * prcp)))

# Plot the distribution of your estimates
pivot_bootstrap_results |> 
  ggplot(aes(x = r.squared)) + 
  geom_histogram()

pivot_bootstrap_results |> 
  ggplot(aes(x = quantity2)) + 
  geom_histogram() + 
  labs(x = "log(beta_hat1*beta_hat2)")
```

**Comments:**

The distribution of r-squared estimates are approximately normal. The r-squared values range from 0.86 to 1 and counts range from 0 to about 490.

The distribution of log(beta_hat1xbeta_hat2) is left skewed. There seems to be outliers based on the histogram.

* Applying log(tmin * prcp) produced NaNs because log cannot be applied to ≤ 0; therefore, I have to explicitly apply to only positive values. Note: there are `sum(is.na(pivot_bootstrap_results[["quantity2"]]))` quantity2 with negative values that we cannot take log of.

* log(beta_hat1*beta_hat2) = quantity2


```{r}
# 95% confidence intervals

# r-squared
pivot_bootstrap_results |> 
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975)) |>   
    knitr::kable()

# quantity2
pivot_bootstrap_results |> 
  summarize(
    ci_lower = quantile(quantity2, 0.025, na.rm = TRUE), 
    ci_upper = quantile(quantity2, 0.975, na.rm = TRUE)) |> 
    knitr::kable()
```
**Comments:**

* r-squared 95% CI: (0.889, 0.941)

* log(beta_hat1*beta_hat2) 95% CI: (-8.98, -4.60)

NAs are ommitted.

The 95% confidence interval for r-squared is **(0.889, 0.941)** and for log(beta_hat1xbeta_hat2) is **(-8.98, -4.60)**.



# Problem 3

In this problem, you will analyze data gathered to understand the effects of several variables on a child’s birthweight. 

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

## load and clean dataset
```{r}
birthweight = 
  read_csv(file = "./data/birthweight.csv") |> 
  janitor::clean_names() |> 
  drop_na() |> 
  mutate(
    babysex = as.factor(babysex),
    frace=recode(frace,"1"="White", "2"="Black", "3"="Asian", "4"="Puerto Rican", '8'="Other", "9"="Unknown"),
    frace = as.factor(frace),
    mrace=recode(mrace,"1" = "White", "2" = "Black", "3" = "Asian", "4"="Puerto Rican", "8"="Other"),
    mrace = as.factor(mrace))
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

### full model
```{r}
full_model = lm(bwt~., data=birthweight)
full_model

summary(full_model) |> 
  broom::tidy() |> 
  select(term, estimate, p.value)
```

### proposed model
```{r}
stepwise_model = lm(bwt~bhead + blength + delwt + fincome + gaweeks + ppwt + smoken, data = birthweight)
stepwise_model

summary(stepwise_model) |> 
  broom::tidy() |> 
  select(term, estimate, p.value)
```
**Comments:**
Variables for the stepwise model were chosen based on eliminating those with large p-value scores --though there is not set definition, I used those with p-value < 0.20. It is also reasonable that a baby's birthweight is related to family monthly income, the baby's measurements, gestational age in weeks, mother's prepregnancy weight and whether the mother smoked during pregnancy.

### predictions vs. residuals plot
```{r}
#birthweight |>
#  modelr::add_residuals(full_model) |>
#  modelr::add_predictions(full_model) |> 
#  ggplot(aes(x = resid, y = pred)) + 
#  geom_point()
```


Compare your model to two others:

* One using length at birth and gestational age as predictors (main effects only)

* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.



















